---
title: 'Peer-graded Assignment: R Markdown and Leaflet'
author: "Charl Marais"
date: "20 April 2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Peer-graded Assignment: R Markdown and Leaflet (and Shiny)

This R Markdown document is made interactive using Shiny. The user can select, from a list of countries and a leaflet map will zoom to the particular country and add a pointer on the 10 largest cities. The pointer will have some key statistics of the capital.

# Load the required libraries
```{r}
library(shiny)
library(maps)
library(leaflet)
```

# Build the ui function

```{r}
ui <- fluidPage(
  selectInput("country", "Please select country : ",
              sort(unique(data.frame(world.cities)$country.etc))),
  leafletOutput("mymap")
)
```

# Build the server function

```{r}
server <- function(input, output) {
  data <- data.frame(world.cities)
  colnames(data)[which(colnames(data) %in% "long")] <- "lng"
  
  dat_fin <- reactive({
    tmp <- data[data$country.etc == input$country, ]
    tmp <- tmp[order(tmp$pop, decreasing = T)[1:10], c("lat", "lng")]
    
    return(tmp)
  })
  
  details <- reactive({paste(dat_fin()$name, "population = ", dat_fin()$pop)})
  
  output$mymap <- renderLeaflet({
    dat_fin() %>%
      leaflet() %>%
      addTiles() %>%
      addMarkers(popup = details())
  })
  
}
```

# Call the Shiny App

```{r}
shinyApp(ui, server)
```



